Title

### 2020-07-28 paper.tex
Adding todo items

%other packages
\usepackage{amsmath}
\usepackage{amssymb}
% \usepackage{physics}

@@

\usepackage{graphicx}

% \usepackage{siunitx}

%\pagestyle{headings}

\title{Paper}
\author{Deepak Mallubhotla}
% want empty date
\date{\today}

@@

\section{Introduction \label{sec:intro}}

>>>>

%other packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{physics}

@@

\usepackage{graphicx}
\usepackage{todonotes}
\usepackage{siunitx}

\title{Title}

@@

\section{Introduction \label{sec:intro}}
\begin{itemize}
	\item Motivate with~\cite{Tenberg2019} and~\cite{Kolkowitz2015}
	\item Existing work with Lindhard expression~\cite{QubitRelax}
	\item Variety of existing superconducting dielectric functions like in~\cite{AGD, llv9, Zimmermann1991, Mattis, Tinkham}.
	Advantage of Nam expression\cite{Nam1967} is that it's got the worked out dependence on momentum and impurities, both of which we need.
\end{itemize}
\section{Methods \label{sec:methods}}

\begin{itemize}
	\item Include Nam expressions from~\cite{Nam1967}, including the choice for particle density function etc.
	\item Are there any interesting plots for Nam dielectric function?
	We're not adding anything to them, so only interesting thing is showing effect of frequency / temperature to show that Nam did indeed describe something that looks like a superconductor.
	\item Potentially include Lindhard expressions for completeness? or does it suffice to mention them.
	\item Include noise expressions from~\cite{QubitRelax} and~\cite{Henkel1999}.
	\item Include the Ford and Weber expressions in~\cite{Ford1984}, for reflection coefficients/ surface impedances.
	\item Include 3D plot of noise vs $\omega$ and $T$ with presence of the phase transition to superconducting state?
	\item Include sample plot of noise vs distance here to show overall shape of noise (e.g. show levelling off for $z \rightarrow 0$ and cubic dependence further away, as expected?).
\end{itemize}

\section{Numerical Techniques \label{sec:technical}}

\begin{itemize}
	\item Limitations on superconducting dielectric function.
	In every expression that's worked out for arbitrary momentum, the large-momentum dependence goes as $\frac{1}{k}$, which is clearly unphysical.
	Issue exists in~\cite{Nam1967, AGD, Tinkham}, etc.
	\item Include description of cutoff process.
	\item Include description of the interpolation process.
	\item Is the numerics of picking the relevant unit scales / discussion of convergence interesting?
	It might be too obvious that the convergence is expected because these are real quantities.
	\item Any other potentially interesting approximations?
	Some integrals have regions entirely discarded because they are too small to matter, which is why the expressions in the Mathematica package are much simpler than what's in Nam.
\end{itemize}

\section{Experiments \label{sec:experiments}}
\begin{itemize}
	\item Show that expression is of right order of magnitude to describe~\cite{Tenberg2019}.
	\item Look at temperature at which~\cite{Tenberg2019} should show SC effects (not far off!)
	\item Compare to~\cite{Kolkowitz2015}?
	Much further from relevant temperature range.
	\item Metal choices?
	Obviously large $T_c$ is most important to get noise reduction benefits.
	What else is most relevant for usable metals?
\end{itemize}
\section{Conclusions \label{sec:conclusions}}
